Elephace: Elephant Re-identification Using Deep Learning

### 2022-05-05 Report/PaperForReview.tex
add references

Animal tracking can be performed by using a device that is attached to the animal. This technique requires human intervention and it is intrusive. It requires capturing animals which can be dangerous and also disruptive for an animal's wild habitat \cite{Deb}. Another method of tracking animals is by capturing the images and re-identifying animals from those images. The re-identification performed manually can be a time consuming process as multiple and vast numbers of images need to be analyzed. This re-identification requires domain knowledge about the particular species and also its prone to biases related to human judgment [Schneider, Stefan, et al.]. \cite{SchneiReidentify}

Automated re-identification of animals provides a better solution to animal tracking without involving disruptive techniques and human errors. There has been ongoing research to extend human face recognition and identification techniques to animal identification using deep learning. There are many challenges while building a state of the art animal re-identification and classification model. These challenges arise due to similar looking animals and very small distinctive features like body size, scars and marks, coloring, etc [Körschens, et al.]. Apart from this, these features could also change over time. For example in the case of elephants, it could lose a tusk and a hole in the ear may become a rip [Körschens, et al.]. Other challenges are variations in image captured such as occlusion, varying viewpoints, different poses and angles of the animal in an image that affect the detection of distinctive features. For example in the case of elephants the feature might not be clearly visible in images because of mud on their bodies or the angle and movement [Körschens, et al.].

@@

For the difficult task of Nyala identification, [Zyl et al] implemented an end to end system consisting of Faster R-CNN model for bounding box detection and then siamese network using ResNet-152 backbone for image embedding. Their top1 accuracy for zebra dataset is 74.1\% and top-10 accuracy of 85\% for Nyala animal identification.

[Freytag et al] uses matrix logarithm transformation on bilinear pooling to increase the discriminability of features in Alexnet and VGGfaces networks. Using these techniques, they achieved the state of the art for chimpanzee faces classification. For a similar task, Gorilla faces classification [Brust et al] uses YOLO and R-CNN for bounding box detention along with AlexNet for feature extraction upon which they used SVM for class label prediction.

>>>>

Animal tracking can be performed by using a device that is attached to the animal. This technique requires human intervention and it is intrusive. It requires capturing animals which can be dangerous and also disruptive for an animal's wild habitat \cite{Deb}. Another method of tracking animals is by capturing the images and re-identifying animals from those images. The re-identification performed manually can be a time consuming process as multiple and vast numbers of images need to be analyzed. This re-identification requires domain knowledge about the particular species and also its prone to biases related to human judgment \cite{SchneiReidentify}.

Automated re-identification of animals provides a better solution to animal tracking without involving disruptive techniques and human errors. There has been ongoing research to extend human face recognition and identification techniques to animal identification using deep learning. There are many challenges while building a state of the art animal re-identification and classification model. These challenges arise due to similar looking animals and very small distinctive features like body size, scars and marks, coloring, etc \cite{Korschens}. Apart from this, these features could also change over time. For example in the case of elephants, it could lose a tusk and a hole in the ear may become a rip \cite{Korschens}. Other challenges are variations in image captured such as occlusion, varying viewpoints, different poses and angles of the animal in an image that affect the detection of distinctive features. For example in the case of elephants the feature might not be clearly visible in images because of mud on their bodies or the angle and movement \cite{Korschens}.

@@

For the difficult task of Nyala identification, [Zyl et al]\cite{Zyl} implemented an end to end system consisting of Faster R-CNN model for bounding box detection and then siamese network using ResNet-152 backbone for image embedding. Their top1 accuracy for zebra dataset is 74.1\% and top-10 accuracy of 85\% for Nyala animal identification.

[Freytag et al]\cite{Freytag} uses matrix logarithm transformation on bilinear pooling to increase the discriminability of features in Alexnet and VGGfaces networks. Using these techniques, they achieved the state of the art for chimpanzee faces classification. For a similar task, Gorilla faces classification [Brust et al]\cite{Brust} uses YOLO and R-CNN for bounding box detention along with AlexNet for feature extraction upon which they used SVM for class label prediction.
